### 2013-09-15 nyu/paper.tex
minor fixes to nyu chapter

\chapter{Learning Depth-Sensitive Conditional Random Fields for Semantic
Segmentation of RGB-D Images}

\section{Introduction}
For robots to perform varied tasks in unstructured environments, understanding their
surroundings is essential. We formulate the problem of semantic annotation of maps
as a dense labeling of RGB-D images into semantic classes. Dense labeling of objects
and structure classes allows for a detailed reasoning about the scene.

@@

\begin{figure}
    \begin{center}
        \includegraphics[width=\linewidth]{nyu/images/teaser}
    \end{center}
    \caption{%
        Overview of the proposed semantic segmentation method.\label{teaser}
    \figlabel{height}}
\end{figure}

@@

\subsection{Unary Image Features}\seclabel{unaries}
Our method builds on the probability output of a random forest, trained for pixel-wise
classification of the structure classes.
We use the GPU implementation provided by \citet{stueckler2013}\footnote{\url{https://github.com/deeplearningais/curfil}}.
The input for training are the full RGB-D images, transformed to Lab
color space. Each tree in the forest uses training pixels only from a subset of
training images. For each training image, an equal number of pixels for each
occurring class is sampled. Split features are given by difference of regions
on color or depth channels. Region size and offsets are normalized using the
depth at the target pixel.
We accumulate the probabilistic output for all pixels within a superpixel, and
use the resulting distribution as a feature for the unary node potentials in our CRF model.
We augment these prediction with another feature, based on the height of a superpixel in 3D.
This is a very informative feature, in particular to determine the floor.
To compute the height of a (super) pixel, we first find the ``up'' direction.
We use a very simple approach that we found effective: we cluster normal
directions of all pixels into 10 clusters using $k$-means, and use the one that
is most parallel to the $Y$ direction, which roughly corresponds to height in
the dataset.
We then project the 3D point cloud given by the depth along this direction, and
normalize the result between $0$ and $1$.
This procedure works robustly given there is some horizontal surface in the image,
such as the ground or a table. A few scenes contain only walls and furniture,
and the approach fails for these. \Figref{height} illustrates a typical case and
one of the much rarer failure cases.
While we could use a more elaborate scheme,
such as the one from \citet{SilbermanECCV12}, we suspect that the feature is of
little use in scenes without horizontal surfaces.
\begin{figure}
    \begin{center}
        \includegraphics[width=\linewidth]{nyu/images/normal_feature}
    \end{center}
    \vspace{-3mm}
    \caption{%
        Visualization of one of the pairwise features, the similarity between superpixel normals.
        The image shows the zoom-in of a bedroom scene, together with the superpixel over-segmentation.
        Lines connect adjacent superpixels, and line-strength gives the magnitude of the orientation similarity.
    \figlabel{normal_feature}}
    \vspace{-9mm}
\end{figure}

@@

\emph{Color Contrast}
    We employ a non-linear color contrast, as is common in the computer
    vision literature, between the superpixel mean colors $c_i$ and $c_j$:
    $\exp\left(-\gamma \lVert c_i - c_j \rVert^2\right)$.

@@

\begin{table*}[t]
    \caption{Quantitative comparison of the proposed method with the
    literature.\tablabel{results}}
\begin{tabularx}{\linewidth}{@{\extracolsep{\fill}}lcccccc}
\toprule
                        & ground        &  structure    & furniture     & props         & class average   & pixel average\\
\cmidrule(r){1-7}

RF                              &         90.8  &   81.6        & 67.9          & 19.9          &  65.0        &  68.3 \\
RF + SP                         &         92.5  &   83.3        & \textbf{73.8} & 13.9          &  65.7        &  70.1 \\ 
RF + SP + SVM                   &         94.4  &   79.1        & 64.2          & \textbf{44.0} &  70.4        &  70.3 \\
RF + SP + CRF                   & \textbf{94.9} &   78.9        &          71.1 & 42.7          &\textbf{71.9} &  \textbf{72.3} \\
\cmidrule(r){1-7}
\citet{SilbermanECCV12}         &         68    &   59          & 70           & 42            &  59.6        & 58.6 \\
\citet{couprie-iclr-13}         &         87.3  & \textbf{86.1} & 45.3         & 35.5          &  63.5        & 64.5 \\
\cmidrule(r){1-7}
\citet{stueckler2013}$^\dagger$ & \textbf{95.6} &   83.0        & \textbf{75.1}& 14.2          &  67.0        & 70.9 \\

\bottomrule
\end{tabularx}
\quad\\The best value in each column is printed in bold$^\dagger$. The upper part of
the table shows contributions by different parts of our pipeline. RF stands for random forest prediction, RF + SP for aggregated
random forests prediction within superpixels, RF + SP + SVM for an SVM trained on the unary potentials, and RF + SP + CRF is
our proposed pipeline. We optimized our approach for class average
accuracy.\\
$^\dagger$ \footnotesize Note that the work of \citet{stueckler2013} is not directly
comparable, as they integrated information over multiple frames, and did not
measure accuracy for pixels without valid depth measurement.
\vspace{-5mm}
\end{table*}

@@

\begin{figure}
    \begin{center}
        \includegraphics[width=.45\linewidth]{nyu/images/vertical_alignment}
    \includegraphics[width=.45\linewidth]{nyu/images/depth_difference}
    \end{center}
    \vspace{-3mm}
    \caption{%
        Visualization of some of the learned potentials. The right potential is
        applied to relative depth between superpixels, the second on the
        feature encoding whether one superpixel is above the other in the
        image. See \secref{results} for details.
    \figlabel{weights}}
    \vspace{-3mm}
\end{figure}

@@

    \includegraphics[width=\linewidth]{nyu/images/00845_gt.png}&%
    \includegraphics[width=\linewidth]{nyu/images/00781_gt.png}&%
    \includegraphics[width=\linewidth]{nyu/images/01331_gt.png}&%
    \includegraphics[width=\linewidth]{nyu/images/00118_gt.png}&%
    \includegraphics[width=\linewidth]{nyu/images/01203_gt.png}\\
    \multicolumn{5}{@{}c@{}}{Ground Truth}\vspace{3mm}\\
    \multicolumn{5}{@{}c@{}}{%
        \includegraphics[]{legend.pdf}
    }
    \end{tabu}
\caption{%
Qualitative evaluation of the CRF\@.
The first three images illustrate errors in the original prediction that can be corrected, while
the second two images illustrate failure modes. Pixels marked as void
are excluded from the evaluation. See the \secref{results} for details.
\figlabel{comparison}}
\end{figure*}

>>>>

\chapter{Learning Depth-Sensitive Conditional Random Fields}

%\section{Introduction}
For robots to perform varied tasks in unstructured environments, understanding their
surroundings is essential. We formulate the problem of semantic annotation of maps
as a dense labeling of RGB-D images into semantic classes. Dense labeling of objects
and structure classes allows for a detailed reasoning about the scene.

@@

\begin{figure}
    \begin{center}
        \includegraphics[width=\linewidth]{nyu/images/teaser}
    \end{center}
    \caption{%
        Overview of the proposed semantic segmentation method.\figlabel{teaser}
    \figlabel{height}}
\end{figure}

@@

\subsection{Unary Image Features}\seclabel{unaries}
Our method builds on the probability output of a random forest, trained for pixel-wise
classification of the structure classes.
We use the GPU implementation provided by \citet{stueckler2013}\footnote{\url{https://github.com/deeplearningais/curfil}}.
The input for training are the full RGB-D images, transformed to Lab
color space. Each tree in the forest uses training pixels only from a subset of
training images. For each training image, an equal number of pixels for each
occurring class is sampled. Split features are given by difference of regions
on color or depth channels. Region size and offsets are normalized using the
depth at the target pixel.
We accumulate the probabilistic output for all pixels within a superpixel, and
use the resulting distribution as a feature for the unary node potentials in our CRF model.
We augment these prediction with another feature, based on the height of a superpixel in 3D.
This is a very informative feature, in particular to determine the floor.
To compute the height of a (super) pixel, we first find the ``up'' direction.
We use a very simple approach that we found effective: we cluster normal
directions of all pixels into 10 clusters using $k$-means, and use the one that
is most parallel to the $Y$ direction, which roughly corresponds to height in
the dataset.
We then project the 3D point cloud given by the depth along this direction, and
normalize the result between $0$ and $1$.
This procedure works robustly given there is some horizontal surface in the image,
such as the ground or a table. A few scenes contain only walls and furniture,
and the approach fails for these. \Figref{height} illustrates a typical case and
one of the much rarer failure cases.
While we could use a more elaborate scheme,
such as the one from \citet{SilbermanECCV12}, we suspect that the feature is of
little use in scenes without horizontal surfaces.
\begin{figure}
    \begin{center}
        \includegraphics[width=\linewidth]{nyu/images/normal_feature}
    \end{center}
    \caption{%
        Visualization of one of the pairwise features, the similarity between superpixel normals.
        The image shows the zoom-in of a bedroom scene, together with the superpixel over-segmentation.
        Lines connect adjacent superpixels, and line-strength gives the magnitude of the orientation similarity.
    \figlabel{normal_feature}}
\end{figure}

@@

\emph{Color Contrast}
    We employ a non-linear color contrast, as is common in the computer
    vision literature, between the superpixel mean colors $c_i$ and $c_j$:
    \[
        \exp\left(-\gamma \lVert c_i - c_j \rVert^2\right).
     \]

@@

\begin{table*}[t]
    \caption{Quantitative comparison of the proposed method with the
    literature.\tablabel{results}}
\begin{tabularx}{\linewidth}{@{\extracolsep{\fill}}l@{}cccccc}
\toprule
                        & \footnotesize{ground}        &  \footnotesize{structure}    & \footnotesize{furniture}     & \footnotesize{props}         & \footnotesize{class avg.}   & \footnotesize{pixel avg.}\\
\cmidrule{1-7}

RF                              &         90.8  &   81.6        & 67.9          & 19.9          &  65.0        &  68.3 \\
RF + SP                         &         92.5  &   83.3        & \textbf{73.8} & 13.9          &  65.7        &  70.1 \\ 
RF + SP + SVM                   &         94.4  &   79.1        & 64.2          & \textbf{44.0} &  70.4        &  70.3 \\
RF + SP + CRF                   & \textbf{94.9} &   78.9        &          71.1 & 42.7          &\textbf{71.9} &  \textbf{72.3} \\
\cmidrule{1-7}
\citet{SilbermanECCV12}         &         68    &   59          & 70           & 42            &  59.6        & 58.6 \\
\citet{couprie-iclr-13}         &         87.3  & \textbf{86.1} & 45.3         & 35.5          &  63.5        & 64.5 \\
\cmidrule{1-7}
\citet{stueckler2013}$^\dagger$ & \textbf{95.6} &   83.0        & \textbf{75.1}& 14.2          &  67.0        & 70.9 \\

\bottomrule
\end{tabularx}
\quad\\The best value in each column is printed in bold$^\dagger$. The upper part of
the table shows contributions by different parts of our pipeline. RF stands for random forest prediction, RF + SP for aggregated
random forests prediction within superpixels, RF + SP + SVM for an SVM trained on the unary potentials, and RF + SP + CRF is
our proposed pipeline. We optimized our approach for class average
accuracy.\\
$^\dagger$ \footnotesize Note that the work of \citet{stueckler2013} is not directly
comparable, as they integrated information over multiple frames, and did not
measure accuracy for pixels without valid depth measurement.
\end{table*}

@@

\begin{figure}
    \begin{center}
        \includegraphics[width=.45\linewidth]{nyu/images/vertical_alignment}
    \includegraphics[width=.45\linewidth]{nyu/images/depth_difference}
    \end{center}
    \caption{%
        Visualization of some of the learned potentials. The right potential is
        applied to relative depth between superpixels, the second on the
        feature encoding whether one superpixel is above the other in the
        image. See \secref{results} for details.
    \figlabel{weights}}
\end{figure}

@@

    \includegraphics[width=\linewidth]{nyu/images/00845_gt.png}&%
    \includegraphics[width=\linewidth]{nyu/images/00781_gt.png}&%
    \includegraphics[width=\linewidth]{nyu/images/01331_gt.png}&%
    \includegraphics[width=\linewidth]{nyu/images/00118_gt.png}&%
    \includegraphics[width=\linewidth]{nyu/images/01203_gt.png}\\
    \multicolumn{5}{@{}c@{}}{Ground Truth}\vspace{3mm}\\
    \multicolumn{5}{@{}c@{}}{%
        \includegraphics[]{nyu/legend.pdf}
    }
    \end{tabu}
\caption{%
Qualitative evaluation of the CRF\@.
The first three images illustrate errors in the original prediction that can be corrected, while
the second two images illustrate failure modes. Pixels marked as void
are excluded from the evaluation. See the \secref{results} for details.
\figlabel{comparison}}
\end{figure*}
